---
title: "FA21 Agency Campaign Vendor Reports"
author: "Office of Marketing and Brand Management"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE,
	fig.width=8, 
	fig.height=1.5
)
```

```{r}
source("C:/Users/christine.iyer/Box/R_Source_Functions/Plot_Table_Functions.R")
```



```{r fig.height=2, fig.width=4}
library(knitr)
library(janitor)
library(tidyr)
library(zoo)
library(lubridate)
library(hms)
library(dplyr)
library(ggplot2)
library(gtable)
library(grid)
library(ggpubr)
library(kableExtra)
library(scales)
library(pander)
```



```{r}
FM <- read.csv("file:///Z:/DAA/Marketing/MKT_output.csv", header = T, stringsAsFactors = F)
#FM <- read.csv("C:/Users/christine.iyer/Box/AnnualCampaignVendorPerformance/MKT_output.csv", header = T, stringsAsFactors = F)
```



```{r}
FM <- FM %>% filter(Master_Adname_Type == "NC" & grepl("21", Code_RecruitingPeriod))
FM <- FM %>% mutate(Code_Audience = ifelse(Master_Adname == "FA20_BR_FB_VID__TL_UG_D_1",  "TL", Code_Audience ), Code_Product = ifelse(Master_Adname == "FA20_BR_FB_VID__TL_UG_D_1",  "UG", Code_Product), Master_Results = as.numeric(Master_Results))
FM <- FM %>% select(1:8, 13, 15:19, 21:24, 26, 28:29, 31:39, 41) %>% select(Master_Date, everything())

```

```{r}
FM <- FM %>% mutate_at(10:31, ~replace(., is.na(.), 0)) %>% mutate(Master_Date = as.Date(Master_Date, format = "%Y-%m-%d")) %>% arrange(Master_Date)
colorP <- c("#F6A704", "#0E1033","#4E7B14","#A92007","#D47E0A")
FMVM <- FM %>%
  mutate(Product_Audience = paste0(Code_Product, "_", Code_Audience)) %>%
  group_by(Code_Audience,Code_Product, Code_Vendor, Code_Medium,Week = as.Date(cut(Master_Date + 1, "week")), format = "%Y-%m-%d") %>%
  summarise(
    Cost = sum(Master_Cost),
    Clicks = sum(Master_Clicks),
    Impressions = round(sum(Master_Impressions),0),
    #CTR = paste0(round(Clicks/Impressions * 100, 2), "%"),
    Bounces = sum(Master_Bounces),
    Sessions = sum(Master_Sessions),
    UPV = sum(Master_Unique_Pageviews),
    Views = sum(Master_Views),
    Completions = sum(Master_Completions),
    #BounceRate = paste0(round(Bounces/Sessions * 100, 2), "%"),
    Step1 = sum(Master_Time_On_Page)/(sum(Master_Pageviews)- sum(Master_Exits)),
    Av_TOP = round_hms(as_hms(Step1), 5),
    ClickRatePct = round(Clicks/Impressions * 100, 2),
    BounceRatePct = round(Bounces/Sessions * 100, 2),
    ViewRate = round(Views/Impressions * 100, 2),
    VTR = round(Completions/Impressions *100, 2),
    ClickableCompletions = sum(Master_Clickable_Completions),
    ClickableCompRate = round(Clicks/ClickableCompletions * 100, 2), 
    Swipes = sum(Master_Swipes), 
    SwipeUpRatePct = round(Swipes/Impressions * 100, 2),
    Opens = sum(Master_Clicks_To_Site),
    CTOR = round(Opens/Clicks * 100, 2), 
    Sends = sum(Master_Sends), 
    LIOpens = sum(Master_Opens),
    LIClicks = sum(Master_Clicks_Sponsored_InMail),
    OpenRate = round(LIOpens/Sends * 100, 2), 
    Engagements = sum(Master_Engagements),
    Results = sum(Master_Results),
    ResultsRate = round(Results/Impressions * 100, 2),
    EngagementRate = round(Engagements/Impressions * 100, 2),
    EngRate = round((sum(LIOpens)+sum(Engagements))/sum(Sends)*100, 2),  
    LICTOR = round(sum(LIClicks)/sum(LIOpens) * 100, 2)) %>%
  select(Week, Impressions, Clicks, Bounces, Sessions, Swipes, ClickRatePct, SwipeUpRatePct, UPV, BounceRatePct, Av_TOP, ClickableCompRate, VTR, CTOR,OpenRate, Sends, ViewRate, ClickableCompletions, Completions, Opens, LIOpens, LIClicks, Engagements, LICTOR, EngRate, EngagementRate, Views, Completions, Results, ResultsRate)


```

### Undergraduate

**Facebook Display**

```{r pressure, echo=FALSE}
IGD <- FMVM %>% 
  filter(Code_Vendor == "FB" &
           Code_Medium == "DISP"  &
           Code_Audience == "HS" &
           Week >= min(Week) & 
           Week <= max(Week)) 
ytd(min(IGD$Week),max(IGD$Week))
FB_DISP_PLT(a)
FB_DISP_TBL(TD)
```

---

**Facebook Video**

```{r echo=FALSE}
IGD <- FMVM %>% 
  filter(Code_Vendor == "FB" &
           Code_Medium == "VID"  &
           Code_Audience == "HS" &
           Week >= min(Week) & 
           Week <= max(Week)) 
ytd(min(IGD$Week),max(IGD$Week))
FB_VID_PLT(a)
FB_VID_TBL(TD)
```

---

**Instagram Display**

```{r}
IGD <- FMVM %>% 
  filter(Code_Vendor == "IG" &
           Code_Medium == "DISP"  &
           Code_Audience == "HS" &
           Week >= min(Week) & 
           Week <= max(Week)) 
ytd(min(IGD$Week),max(IGD$Week))
IG_DISP_PLT(a)
IG_DISP_TBL(TD)
```

---

**Instagram Video**

```{r}
IGD <- FMVM %>% 
  filter(Code_Vendor == "IG" &
           Code_Medium == "VID"  &
           Code_Audience == "HS" &
           Week >= min(Week) & 
           Week <= max(Week)) 
ytd(min(IGD$Week),max(IGD$Week))
IG_VID_PLT(a)
IG_VID_TBL(TD)
```

---

**Instagram Stories**

```{r}
IGD <- FMVM %>% 
  filter(Code_Vendor == "IG" &
           Code_Medium == "ST"  &
           Code_Audience == "HS" &
           Week >= min(Week) & 
           Week <= max(Week)) 
ytd(min(IGD$Week),max(IGD$Week))
IG_VID_PLT(a)
IG_VID_TBL(TD)
```

---

**Programmatic Display**

```{r}
IGD <- FMVM %>% 
  filter(Code_Vendor == "DBM" &
           Code_Medium == "DISP"  &
           Code_Audience == "HS" &
           Week >= min(Week) & 
           Week <= max(Week)) 
ytd(min(IGD$Week),max(IGD$Week))
DBM_DISP_PLT(a)
DBM_DISP_TBL(TD)
```

---

**Pinterest Display**

```{r}
IGD <- FMVM %>% 
  filter(Code_Vendor == "PIN" &
           Code_Medium == "DISP"  &
           Code_Audience == "IN" &
           Week >= min(Week) & 
           Week <= max(Week)) 
ytd(min(IGD$Week),max(IGD$Week))
PIN_DISP_PLT(a)
PIN_DISP_TBL(TD)

```

---

**Pinterest Video**

```{r}
IGD <- FMVM %>% 
  filter(Code_Vendor == "PIN" &
           Code_Medium == "VID"  &
           Code_Audience == "IN" &
           Week >= min(Week) & 
           Week <= max(Week)) 
ytd(min(IGD$Week),max(IGD$Week))
PIN_DISP_PLT(a)
PIN_DISP_TBL(TD)

```

---

**Snapchat Video**

```{r}
IGD <- FMVM %>% 
  filter(Code_Vendor == "SC" &
           Code_Medium == "VID"  &
           Code_Audience == "HS" &
           Week >= min(Week) & 
           Week <= max(Week)) 
ytd(min(IGD$Week),max(IGD$Week))
SC_VID_PLT(a)
SC_VID_TBL(TD)

```

---

### Transfer

**Programmatic Display**

```{r}
IGD <- FMVM %>% 
  filter(Code_Vendor == "DBM" &
           Code_Medium == "DISP"  &
           Code_Audience == "CU" &
           Week >= min(Week) & 
           Week <= max(Week)) 
ytd(min(IGD$Week),max(IGD$Week))
DBM_DISP_PLT(a)
DBM_DISP_TBL(TD)
```


**Facebook Video**

```{r echo=FALSE}
IGD <- FMVM %>% 
  filter(Code_Vendor == "FB" &
           Code_Medium == "VID"  &
           Code_Audience == "CU" &
           Week >= min(Week) & 
           Week <= max(Week)) 
ytd(min(IGD$Week),max(IGD$Week))
FB_VID_PLT(a)
FB_VID_TBL(TD)
```

---

**Instagram Video**

```{r}
IGD <- FMVM %>% 
  filter(Code_Vendor == "IG" &
           Code_Medium == "VID"  &
           Code_Audience == "CU" &
           Week >= min(Week) & 
           Week <= max(Week)) 
ytd(min(IGD$Week),max(IGD$Week))
IG_VID_PLT(a)
IG_VID_TBL(TD)
```

---

**Instagram Stories**

```{r}
IGD <- FMVM %>% 
  filter(Code_Vendor == "IG" &
           Code_Medium == "ST"  &
           Code_Audience == "CU" &
           Week >= min(Week) & 
           Week <= max(Week)) 
ytd(min(IGD$Week),max(IGD$Week))
IG_VID_PLT(a)
IG_VID_TBL(TD)
```

---


**Snapchat Video**

```{r}
IGD <- FMVM %>% 
  filter(Code_Vendor == "SC" &
           Code_Medium == "VID"  &
           Code_Audience == "CU" &
           Week >= min(Week) & 
           Week <= max(Week)) 
ytd(min(IGD$Week),max(IGD$Week))
SC_VID_PLT(a)
SC_VID_TBL(TD)
```

---

### Degree Completion

**Programmatic Display**

```{r}
IGD <- FMVM %>% 
  filter(Code_Vendor == "DBM" &
           Code_Medium == "DISP"  &
           Code_Product == "DC" &
           Week >= min(Week) & 
           Week <= max(Week)) 
ytd(min(IGD$Week),max(IGD$Week))
DBM_DISP_PLT(a)
DBM_DISP_TBL(TD)
```

---

**Facebook Video**

```{r echo=FALSE}
IGD <- FMVM %>% 
  filter(Code_Vendor == "FB" &
           Code_Medium == "VID"  &
           Code_Product == "DC" &
           Week >= min(Week) & 
           Week <= max(Week)) 
ytd(min(IGD$Week),max(IGD$Week))
FB_VID_PLT(a)
FB_VID_TBL(TD)
```

---

**Instagram Video**

```{r}
IGD <- FMVM %>% 
  filter(Code_Vendor == "IG" &
           Code_Medium == "VID"  &
           Code_Product == "DC" &
           Week >= min(Week) & 
           Week <= max(Week)) 
ytd(min(IGD$Week),max(IGD$Week))
IG_VID_PLT(a)
IG_VID_TBL(TD)
```

---

**Gmail InBox**

```{r echo=FALSE}
IGD <- FMVM %>% 
  filter(Code_Vendor == "GM" &
           Code_Medium == "TEXT"  &
           Code_Product == "DC" &
           Week >= min(Week) & 
           Week <= max(Week)) 
ytd(min(IGD$Week),max(IGD$Week))
GM_DISP_PLT(a)
GM_DISP_TBL(TD)
```

---

**LinkedIn Sponsored InMail**

```{r}
IGD <- FMVM %>% 
  filter(Code_Vendor == "LI" &
           Code_Medium == "TEXT"  &
           Code_Product == "DC" &
           Week >= min(Week) & 
           Week <= max(Week)) 
ytd(min(IGD$Week),max(IGD$Week))
LI_TEXT_PLT(a)
LI_TEXT_TBL(TD)
```

---

### Graduate

**Programmatic Display**

```{r}
IGD <- FMVM %>% 
  filter(Code_Vendor == "DBM" &
           Code_Medium == "DISP"  &
           Code_Product == "GR" &
           Week >= min(Week) & 
           Week <= max(Week)) 
ytd(min(IGD$Week),max(IGD$Week))
DBM_DISP_PLT(a)
DBM_DISP_TBL(TD)
```

---

**Facebook Video**

```{r echo=FALSE}
IGD <- FMVM %>% 
  filter(Code_Vendor == "FB" &
           Code_Medium == "VID"  &
           Code_Product == "GR" &
           Week >= min(Week) & 
           Week <= max(Week)) 
ytd(min(IGD$Week),max(IGD$Week))
FB_VID_PLT(a)
FB_VID_TBL(TD)
```

---

**Instagram Video**

```{r}
IGD <- FMVM %>% 
  filter(Code_Vendor == "IG" &
           Code_Medium == "VID"  &
           Code_Product == "GR" &
           Week >= min(Week) & 
           Week <= max(Week)) 
ytd(min(IGD$Week),max(IGD$Week))
IG_VID_PLT(a)
IG_VID_TBL(TD)
```


---

**LinkedIn Sponsored InMail**

```{r}
IGD <- FMVM %>% 
  filter(Code_Vendor == "LI" &
           Code_Medium == "TEXT"  &
           Code_Product == "GR" &
           Week >= min(Week) & 
           Week <= max(Week)) 
ytd(min(IGD$Week),max(IGD$Week))
LI_TEXT_PLT(a)
LI_TEXT_TBL(TD)
```

